Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-10 chi2013-webbox.tex
mum edits ps2

\subsection{PS.2 - Technical Challenges of Data Integration}
Our analysis of structured data feeds started with identifying a set of candidate sources to examine.  We consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb: \url{http://www.programmableweb.com/apis/directory}} list of most popular data feeds for this purpose.  To examine the many varieties of personal data sources, we selected from 5 categories: social network services, retailers, online event calendars, music sites, and weather, selecting 2--5 sources from each, for a total of 20.

@@

\subsubsection{Results}
While most of the data records were small and relatively simple, nearly one in each category was substantially larger and more complex. In particular, Amazon, Soundcloud, Twitter and Weather Underground were the most complex in each of their respective categories. Mapping equivalent properties among the instance records for each category revealed little overall overlap among records, except among the smallest records (which had few properties to begin with).  This finding suggests that consolidating such records would effectively substantially increase the amount of information held by each.  While some of these `unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties that were simply absent in other sources' records.  For example, among the 4 music data providers examined, only Spotify listed the source album that featured a particular song.  Such omissions reveal that data APIs often reflect each provider's own specific needs, and that integrating information across multiple sources may often be necessary to create more complete and useful representations.

The second finding is that equivalent properties were only rarely given the same name; thus, terminological (or naming) heterogeneity was prevalent across nearly all records observed.  Structural inconsistencies were rarer, with the most common case occuring where a record that represented a value as a simple literal was expanded out in another as an entire sub-structure.  This most commonly occurred for fields with common string serialisations, such as dates, prices, and intervals.  Meanwhile, examples of modelling differences were rarer than those of structural heterogeneity, with the few we found mostly being attributed to concepts on one site not mapping perfectly to those of another site, and differences in units of measurement.
% We also encountered two examples of records in which multiple data fields were nested as a single literal, textual ``description'' field.  This behaviour stems from the intended use of such records only by human readers, rather than in structured data applications.

>>>>

\subsection{PS.2 - Technical Challenges of Data Integration}
For Pre-Study 2, our analysis of structured data feeds started with identifying a set of candidate sources to examine.  We consulted the ProgrammableWeb API directory\footnote{ProgrammableWeb: \url{http://www.programmableweb.com/apis/directory}} list of most popular data feeds for this purpose.  To examine the many varieties of personal data sources, we selected from 5 categories: social network services, retailers, online event calendars, music sites, and weather, selecting 2--5 sources from each, for a total of 20.

@@

\subsubsection{Results}
While most of the data records examined in PS.2 were small and relatively simple, nearly one in each category was substantially larger and more complex. In particular, Amazon, Soundcloud, Twitter and Weather Underground were the most complex in each of their respective categories. Mapping equivalent properties among the instance records for each category revealed little overall overlap, except among the smallest records (which had few properties to begin with).  This finding suggests that consolidating such records would substantially increase the amount of information held by each.  Some of the unique properties were primarily for internal use (such as service-specific IDs).  Some, however, contained useful properties which were simply absent in alternate sources.  For example, among the 4 music data providers examined, only Spotify listed the source album that featured a particular song.  Such omissions revealed that data APIs often were reflective of each provider's own specific needs, necessitating the integration of information across multiple sources to create more complete and useful representations.

A second observation is that equivalent properties were only rarely given the same name; thus, terminological (or naming) heterogeneity was prevalent across nearly all records observed.  Structural inconsistencies were rarer, with the most common case occuring where a record that represented a value as a simple literal was expanded out in another as an entire sub-structure.  This most commonly occurred for fields with common string serialisations, such as dates, prices, and intervals.  Meanwhile, examples of modelling differences were rarer than those of structural heterogeneity, with the few we found mostly being attributed to concepts on one site not mapping perfectly to those of another site, and differences in units of measurement.
% We also encountered two examples of records in which multiple data fields were nested as a single literal, textual ``description'' field.  This behaviour stems from the intended use of such records only by human readers, rather than in structured data applications.
